---
title: "Gapminder analysis"
author: "Weili"
date: "10/14/2019"
output:
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
    
---

#Introduction

Here is my first rmd document

#Let's embed some r code

we'll write an R chunck that loads the tidyverse package and reads in the Gapminder data set from the data subdirectory of the project

CMD+OPT+i quick keys to insert new r chunck
```{r}
library(tidyverse, quietly = TRUE)
gm <- read_csv("Data/gapminder.csv")

```
#Investigate gm data

Let's take a look at the gm

```{r}
head(gm)
```
#our first plot
Show gdp per captia on x and life expectancy on y

```{r, fig.cap="Life Expectancy v.GDP with color", fig.width=3}
ggplot(gm, aes(x=gdpPercap, y= lifeExp)) + 
  geom_point(aes(col = continent)) + 
  scale_x_log10()
```
# Possible chunk options

Options include:
- echo (TRUE by default) whether to include code in output
- results
  - hide will hide the results
  - hold will hold results until end of r chunk
- include (True by default) if FALSE then the code will not be run
-fig.width, fig.height set the figure dimensions int the output
-cache (FALSE by default) if TRUE saves the result from r chunk

#Table in RMarkdown

See some data using head
```{r}
head(gm)
```
now head function as a nicely formatted table
```{r}
library(knitr)
kable(head(gm))
```

If you like tables, look at **gt** table package

! sh: pdflatex: command not found

